Designing and Developing a Personalised Recommender System

### 2021-02-10 paper/paper.tex
added ability to give rating

\author{\IEEEauthorblockN{Thomas Butterfield}
\IEEEauthorblockA{\textit{dept. Computer Science} \\
\textit{Durham University}\\
Durham, United Kingdom \\
thomas.butterfield@durham.ac.uk}
}

@@

\subsection{Input interface}
The input interface is the command line.
The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.

>>>>

\author{\IEEEauthorblockN{lrfk99}
\IEEEauthorblockA{\textit{dept. Computer Science} \\
\textit{Durham University}\\
Durham, United Kingdom}
}

@@

\subsection{Input interface}
The system has a command line based interface, so all user input of the input is given via the command line. 
The system recognises the active user by their unique user ID, some example IDs are provided in the 'README.txt' 
file for testing and demonstration purposes. 
Only explicit user data is gathered in order to make the system more explainable and transparent, 
and users are made aware of which data is collected, how it is collected, and for which purposes. 
This data includes the user's nearest city (of the 10 available) and the type of food that 
they are in the mood for. 
The user is able to change these choices from the main menu, as well as switch to a different user 
for testing purposes. 
When the user is presented with a list of recommendations, they can then choose one that they want 
to see more information about and from here they can leave a rating, return to the list, or return to 
the main menu. 
User profiles can be updated by giving a rating of a restaurant through the system. 
Any rating given will affect future recommendations given by the system to that user 
and to other similar users.

The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.
